---
title: "Week-5: Code-along"
author: "Insert your name here"
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
pdf_document: default
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Writing a function
<br>

### 1. Write a function to print a "Hello" message (Slide #14)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 2. Function call with different input names (Slide #15)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 3. typeof primitive functions (Slide #16)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 4. typeof user-defined functions (Slide #17)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 5. Function to calculate mean of a sample (Slide #19)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 6. Test your function (Slide #22)

```{r, eval=FALSE,echo=TRUE}
# With one input

```
<br>
```{r, eval=FALSE,echo=TRUE}
# With vector input

```
<br>

### 7. Customizing the function to suit input (Slide #23)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 8. Setting defaults (Slide #25)

```{r, eval=FALSE,echo=TRUE}
# First define the function

# Call the function 
```
<br>

### 9. Different input combinations (Slide #26)

```{r, eval=FALSE,echo=TRUE}
# Enter code here 
```
<br>

### 10. Different input combinations (Slide #27)

```{r, eval=FALSE,echo=TRUE,error=FALSE} 
# set error=TRUE to see the error message in the output
# Enter code here 
```
<br>

### 11. Some more examples (Slide #28)

```{r, eval=FALSE,echo=TRUE,error=FALSE} 
# Enter code here 
```
<br>

## B. Scoping
<br>

### 12. Multiple assignment of z (Slide #36)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>

### 13. Multiple assignment of z (Slide #37)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```
<br>